---
title: "Changing the Proportion of Non-Nulls"
subtitle: "Comparison of Offline and Online"
author: "Lathan Liou"
output: 
  html_document:
    keep_md: true
  pdf_document:
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      dev = "tiff")
library(tidyverse)
library(data.table)
library(ggsci)
library(fs)

#load data
all_pi_sim_data <- map(list.files(path = "change_pi_sim", 
                                  pattern = "change_pi_run_fc1.5_b25",
                                  full.names = TRUE), readRDS)

# Data Key
## primary = power, fdr
## secondary = tnr, ppv
## component = tp, fp, tn, fn

primary_means <- rbindlist(all_pi_sim_data)[,lapply(.SD, mean, na.rm = TRUE), list(pi)] %>%
  select(pi, contains("power")|contains("fdr")) %>%
  pivot_longer(cols = contains("power"),
               names_to = "method",
               names_prefix = "power_",
               values_to = "power") %>%
  pivot_longer(cols = contains("fdr"),
               names_to = "method2",
               names_prefix = "fdr_",
               values_to = "fdr")

primary_lower_bounds <- rbindlist(all_pi_sim_data)[,lapply(.SD, quantile, probs = 0.025, na.rm = TRUE), list(pi)] %>%
  select(pi, contains("power")|contains("fdr")) %>%
  pivot_longer(cols = contains("power"),
               names_to = "method",
               names_prefix = "power_",
               values_to = "power") %>%
  pivot_longer(cols = contains("fdr"),
               names_to = "method2",
               names_prefix = "fdr_",
               values_to = "fdr") %>%
  rename(lower_power = power,
         lower_fdr = fdr)

primary_upper_bounds <- rbindlist(all_pi_sim_data)[,lapply(.SD, quantile, probs = 0.975, na.rm = TRUE), list(pi)] %>%
  select(pi, contains("power")|contains("fdr")) %>%
  pivot_longer(cols = contains("power"),
               names_to = "method",
               names_prefix = "power_",
               values_to = "power") %>%
  pivot_longer(cols = contains("fdr"),
               names_to = "method2",
               names_prefix = "fdr_",
               values_to = "fdr") %>%
  rename(upper_power = power,
         upper_fdr = fdr)

# primary_sds <- rbindlist(all_pi_sim_data)[,lapply(.SD, sd, na.rm = TRUE), list(pi)] %>%
#     select(pi, contains("power")|contains("fdr")) %>%
#     pivot_longer(cols = contains("power"),
#                names_to = "method",
#                names_prefix = "power_",
#                values_to = "power") %>%
#   pivot_longer(cols = contains("fdr"),
#                names_to = "method2",
#                names_prefix = "fdr_",
#                values_to = "fdr") %>%
#   rename(sd_power = power,
#          sd_fdr = fdr)

primary_data <- bind_cols(primary_means,
                          primary_lower_bounds %>% select(lower_power, lower_fdr),
                          primary_upper_bounds %>% select(upper_power, upper_fdr)) %>%
  mutate(method = case_when(method == "0.025" ~ "Uncorrected 0.025",
                            method == "0.05" ~ "Uncorrected 0.05",
                            method == "0.1" ~ "Uncorrected 0.1",
                            method == "off_bh" ~ "Offline BH",
                            method == "off_stbh" ~ "Offline StBH",
                            method == "pool_bh" ~ "Appended BH",
                            method == "pool_stbh" ~ "Appended StBH",
                            method == "on_bh" ~ "onlineBH",
                            method == "on_prds" ~ "onlinePRDS",
                            method == "on_stbh" ~ "onlineStBH"),
         method2 = case_when(method2 == "0.025" ~ "Uncorrected 0.025",
                             method2 == "0.05" ~ "Uncorrected 0.05",
                             method2 == "0.1" ~ "Uncorrected 0.1",
                             method2 == "off_bh" ~ "Offline BH",
                             method2 == "off_stbh" ~ "Offline StBH",
                             method2 == "pool_bh" ~ "Appended BH",
                             method2 == "pool_stbh" ~ "Appended StBH",
                             method2 == "on_bh" ~ "onlineBH",
                             method2 == "on_prds" ~ "onlinePRDS",
                             method2 == "on_stbh" ~ "onlineStBH"),
         method_type = as.factor(case_when(str_detect(method, "online") ~ "Online",
                                           str_detect(method, "Appended") ~ "Appended",
                                           str_detect(method, "Offline") ~ "Offline",
                                           str_detect(method, "Uncorrected") ~ "Uncorrected")),
         method_type2 = as.factor(case_when(str_detect(method2, "online") ~ "Online",
                                            str_detect(method2, "Appended") ~ "Appended",
                                            str_detect(method2, "Offline") ~ "Offline",
                                            str_detect(method2, "Uncorrected") ~ "Uncorrected"))
  )

# Set consistent Color Palette

pal <- c("#C0392B", "#2980B9", "#EC7063", "#9B59B6", "#3498DB", "hotpink", "#16A085", "red", "#E67E22", "#34495E") %>%
  setNames(unique(primary_data$method))

# pal <- pal_npg("nrc")(10) %>%
#   setNames(unique(primary_data$method))
# 
# pal <- scales::hue_pal()(10) %>% 
#   setNames(unique(primary_data$method))

# Set consistent plot theme
theme_gen <- function() {
  theme_bw() %+replace%
    theme(
      legend.title = element_text(size = rel(1.5), face = "bold"),
      legend.text = element_text(size = rel(1)),
      legend.title.align = 0,
      axis.title = element_text(size = rel(1.5), face = "bold"),
      axis.text = element_text(size = rel(1))
    )
}
```

# Simulation Settings

* RNAseq data was simulated as described in Soneson et. al. 2013 using the `compcodeR` package
* A fold change of 1.5 and 5 samples were used 
* limma-voom was the method used for differential expression (other data processing steps were selected based on accepted practices)
* A batch size of 10000 was chosen to represent a Seq experiment (realistically, this number is closer to 20000)
* An aggressive gammai sequence of $(0.5, 0.5, 0, ..., 0)$ was selected as per Trnic et. al.'s recommendation for large batch sizes
* 100 trials were performed

# Visualizing Power

```{r change_prop_power_1.5_supp, fig.width = 12, fig.height = 8}
ggplot(primary_data %>% filter(method_type != "Appended"), aes(x = pi, y = power)) + 
  geom_line(aes(col = method,
                linetype = method_type),
            size = 1) + 
  geom_ribbon(aes(ymin = lower_power, ymax = upper_power, fill = method), alpha = 0.2) + 
  theme_bw() + 
  ylim(c(0,1)) + 
  labs(x = "Proportion of DE Genes",
       y = "Power",
       col = "Method",
       linetype = "Method Type") +
  scale_color_manual(
    values = pal,
    limits = force
  ) +
  scale_linetype_discrete(
    limits = force
  ) +
  scale_fill_manual(
    values = pal
  ) + 
  guides(fill = "none") +
  theme_gen()
```

```{r change_prop_power_1.5_supp2, fig.width = 12, fig.height = 8, eval=FALSE}
ggplot(primary_data %>%
         filter(!method %in% c("Uncorrected 0.025", "Uncorrected 0.05", "Uncorrected 0.1", "BatchPRDS")),
       aes(x = pi, y = power)) + 
  geom_line(aes(col = method,
                linetype = method_type),
            size = 1) + 
  geom_ribbon(aes(ymin = lower_power, ymax = upper_power, fill = method), alpha = 0.2) + 
  theme_bw() + 
  labs(x = "Proportion of DE Genes",
       y = "Power",
       col = "Method",
       linetype = "Method Type") +
  scale_color_manual(
    values = pal,
    limits = force
  ) +
  scale_linetype_discrete(
    limits = force
  ) +
  scale_fill_manual(
    values = pal
  ) +
  guides(fill = "none") +
  xlim(0.1, 0.5) +
  ylim(0.65, 0.92) +
  theme_gen()
```

```{r change_prop_power_1.5, fig.width = 12, fig.height = 8}
ggplot(primary_data %>%
         filter(method_type != "Appended", 
                method_type != "Uncorrected"),
       aes(x = pi, y = power)) + 
  geom_line(aes(col = method,
                linetype = method_type),
            size = 1) + 
  geom_ribbon(aes(ymin = lower_power, ymax = upper_power, fill = method), alpha = 0.2) + 
  theme_bw() + 
  labs(x = "Proportion of DE Genes",
       y = "Power",
       col = "Method",
       linetype = "Method Type") +
  scale_color_manual(
    values = pal,
    limits = force
  ) +
  scale_fill_manual(
    values = pal
  ) +
  scale_linetype_discrete(
    limits = force
  ) +
  guides(fill = "none") +
  theme_gen()
```

Observations:

* PRDS is conservative
* Appended has greater power at $\pi$ less than $0.17$ but is surpassed by BatchStBH greater than $0.17$
* BatchBH power approaches Appended power at higher $\pi$

# Visualizing FDR

```{r change_prop_fdr_1.5_supp, fig.width = 12, fig.height = 8}
ggplot(primary_data %>% 
         filter(method_type2 != "Appended"), aes(x = pi, y = fdr)) + 
  geom_line(aes(col = method2,
                linetype = method_type2),
            size = 1) +
  geom_ribbon(aes(ymin = lower_fdr, ymax = upper_fdr, fill = method2), alpha = 0.2) + 
  theme_bw() + 
  geom_hline(yintercept = 0.05, col = "black") +
  labs(x = "Proportion of DE Genes",
       y = "FDR",
       col = "Method",
       linetype = "Method Type") +
  scale_color_manual(
    values = pal,
    limits=force
  ) +
  scale_fill_manual(
    values = pal
  ) +
  scale_linetype_discrete(
    limits = force
  ) +
  guides(fill = "none") +
  theme_gen()
```

Let's zoom in:

```{r change_prop_fdr_1.5, fig.width = 12, fig.height = 8}
ggplot(primary_data %>% 
         filter(!method_type2 == "Uncorrected",
                !method_type2 == "Appended",
                pi != 0), aes(x = pi, y = fdr)) + 
  geom_line(aes(col = method2,
                linetype = method_type2),
            size = 1) + 
  geom_ribbon(aes(ymin = lower_fdr, ymax = upper_fdr, fill = method2), alpha = 0.2) + 
  theme_bw() + 
  geom_hline(yintercept = 0.05, col = "black") +
  labs(x = "Proportion of DE Genes",
       y = "FDR",
       col = "Method",
       linetype = "Method Type") +
  scale_color_manual(
    values = pal,
    limits = force
  ) +
  scale_fill_manual(
    values = pal
  ) +
  scale_linetype_discrete(
    limits = force
  ) +
  guides(fill = "none") +
  theme_gen()
```

Observations:

* FDR is controlled (at the nominal level of 0.05) for BatchBH and BatchPRDS
* Both offline applications (naive and Appended BH) have widely variable control especially at low $\pi$, which results in failure to control FDR at nominal level.
* BatchPRDS is also more variable at small $\pi$ but is overall very conservative, so it still controls FDR at nominal level. 
* BatchStBH inflates FDR beyond $\pi = 0.4$

# Visualizing PPV

```{r, eval=FALSE}
#prep PPV data
secondary_means <- rbindlist(all_pi_sim_data)[,lapply(.SD, mean, na.rm = TRUE), list(pi)] %>%
  select(pi, contains("ppv")) %>%
  pivot_longer(cols = contains("ppv"),
               names_to = "method",
               names_prefix = "ppv_",
               values_to = "ppv")

secondary_lower_bounds <- rbindlist(all_pi_sim_data)[,lapply(.SD, quantile, probs = 0.025, na.rm = TRUE), list(pi)] %>%
  select(pi, contains("ppv")) %>%
  pivot_longer(cols = contains("ppv"),
               names_to = "method",
               names_prefix = "ppv_",
               values_to = "ppv") %>%
  rename(lower_ppv = ppv)

secondary_upper_bounds <- rbindlist(all_pi_sim_data)[,lapply(.SD, quantile, probs = 0.975, na.rm = TRUE), list(pi)] %>%
  select(pi, contains("ppv")) %>%
  pivot_longer(cols = contains("ppv"),
               names_to = "method",
               names_prefix = "ppv_",
               values_to = "ppv") %>%
  rename(upper_ppv = ppv)

# secondary_sds <- rbindlist(all_pi_sim_data)[,lapply(.SD, sd, na.rm = TRUE), list(pi)] %>%
#   select(pi, contains("ppv")) %>%
#   pivot_longer(cols = contains("ppv"),
#                names_to = "method",
#                names_prefix = "ppv_",
#                values_to = "ppv") %>%
#   rename(sd_ppv = ppv)

secondary_data <- bind_cols(secondary_means, 
                            secondary_lower_bounds %>% select(lower_ppv),
                            secondary_upper_bounds %>% select(upper_ppv)) %>%
  mutate(method = case_when(method == "0.025" ~ "Uncorrected 0.025",
                            method == "0.05" ~ "Uncorrected 0.05",
                            method == "0.1" ~ "Uncorrected 0.1",
                            method == "off_bh" ~ "Offline BH",
                            method == "off_stbh" ~ "Offline StBH",
                            method == "pool_bh" ~ "Appended BH",
                            method == "pool_stbh" ~ "Appended StBH",
                            method == "on_bh" ~ "BatchBH",
                            method == "on_prds" ~ "BatchPRDS",
                            method == "on_stbh" ~ "BatchStBH"),
         method_type = as.factor(case_when(str_detect(method, "Batch") ~ "Batch",
                                           str_detect(method, "Appended") ~ "Appended",
                                           str_detect(method, "Offline") ~ "Offline",
                                           str_detect(method, "Uncorrected") ~ "Uncorrected"))
  )
```

```{r change_prop_ppv_1.5_supp, fig.width = 12, fig.height = 8, eval=FALSE}
ggplot(secondary_data, aes(x = pi, y = ppv)) + 
  geom_line(aes(col = method,
                linetype = method_type),
            size = 1) + 
  geom_ribbon(aes(ymin = lower_ppv, ymax = upper_ppv, fill = method), alpha = 0.2) + 
  theme_bw() +
  labs(x = "Proportion of DE Genes",
       y = "PPV",
       col = "Method",
       linetype = "Method Type") +
  scale_color_manual(
    values = pal
  ) +
  scale_fill_manual(
    values = pal
  ) +
  scale_linetype_discrete(
    limits = force
  ) +
  guides(fill = "none") +
  theme_gen()
```

Let's zoom in:

```{r change_prop_ppv_1.5, fig.width = 12, fig.height = 8, eval=FALSE}
ggplot(secondary_data %>% 
         filter(pi > 0,
                !method %in% c("Uncorrected 0.025", "Uncorrected 0.05", "Uncorrected 0.1")), 
       aes(x = pi, y = ppv)) + 
  geom_line(aes(col = method,
                linetype = method_type),
            size = 1) + 
  geom_ribbon(aes(ymin = lower_ppv, ymax = upper_ppv, fill = method), alpha = 0.2) + 
  theme_bw() +
  labs(x = "Proportion of DE Genes",
       y = "PPV",
       col = "Method",
       linetype = "Method Type") +
  scale_color_manual(
    values = pal,
    limits = force
  ) +
  scale_fill_manual(
    values = pal
  ) +
  scale_linetype_discrete(
    limits = force
  ) +
  guides(fill = "none") +
  theme_gen()
```

# Reordered Batches

This simulation reflects scenarios where inherently more powerful more batches (higher $\pi$) are followed by regular batches.

The scenarios were simulated according to the following parameters:

```{r, echo=FALSE}
tibble(family = rep(50, 5),
       super_batch = rep(10, 5),
       super_batch_pi = c(0.3, 0.3, 0.5, 0.5, 0.5),
       reg_batch = rep(40, 5),
       reg_batch_pi = c(0.05, 0.275, 0.25, 0.375, 0.5),
       overall_pi = c(0.1, 0.2, 0.3, 0.4, 0.5))
```

```{r, echo=FALSE}
all_pi_sim_data2 <- map(list.files(path = "change_pi_sim",
                                   pattern = "change_pi_run_reorder1.5_",
                                   full.names = TRUE), readRDS)

primary_means2 <- rbindlist(all_pi_sim_data2)[,lapply(.SD, mean, na.rm = TRUE), list(pi)] %>%
  select(pi, contains("power")|contains("fdr")) %>%
  pivot_longer(cols = contains("power"),
               names_to = "method",
               names_prefix = "power_",
               values_to = "power") %>%
  pivot_longer(cols = contains("fdr"),
               names_to = "method2",
               names_prefix = "fdr_",
               values_to = "fdr")

primary_lower_bounds2 <- rbindlist(all_pi_sim_data2)[,lapply(.SD, quantile, probs = 0.025, na.rm = TRUE), list(pi)] %>%
  select(pi, contains("power")|contains("fdr")) %>%
  pivot_longer(cols = contains("power"),
               names_to = "method",
               names_prefix = "power_",
               values_to = "power") %>%
  pivot_longer(cols = contains("fdr"),
               names_to = "method2",
               names_prefix = "fdr_",
               values_to = "fdr") %>%
  rename(lower_power = power,
         lower_fdr = fdr)

primary_upper_bounds2 <- rbindlist(all_pi_sim_data2)[,lapply(.SD, quantile, probs = 0.975, na.rm = TRUE), list(pi)] %>%
  select(pi, contains("power")|contains("fdr")) %>%
  pivot_longer(cols = contains("power"),
               names_to = "method",
               names_prefix = "power_",
               values_to = "power") %>%
  pivot_longer(cols = contains("fdr"),
               names_to = "method2",
               names_prefix = "fdr_",
               values_to = "fdr") %>%
  rename(upper_power = power,
         upper_fdr = fdr)

primary_data2 <- bind_cols(primary_means2,
                           primary_lower_bounds2 %>% select(lower_power, lower_fdr),
                           primary_upper_bounds2 %>% select(upper_power, upper_fdr)) %>%
  mutate(method = case_when(method == "0.025" ~ "Uncorrected 0.025",
                            method == "0.05" ~ "Uncorrected 0.05",
                            method == "0.1" ~ "Uncorrected 0.1",
                            method == "off_bh" ~ "Offline BH",
                            method == "off_stbh" ~ "Offline StBH",
                            method == "pool_bh" ~ "Appended BH",
                            method == "pool_stbh" ~ "Appended StBH",
                            method == "on_bh" ~ "onlineBH",
                            method == "on_prds" ~ "onlinePRDS",
                            method == "on_stbh" ~ "onlineStBH"),
         method2 = case_when(method2 == "0.025" ~ "Uncorrected 0.025",
                             method2 == "0.05" ~ "Uncorrected 0.05",
                             method2 == "0.1" ~ "Uncorrected 0.1",
                             method2 == "off_bh" ~ "Offline BH",
                             method2 == "off_stbh" ~ "Offline StBH",
                             method2 == "pool_bh" ~ "Appended BH",
                             method2 == "pool_stbh" ~ "Appended StBH",
                             method2 == "on_bh" ~ "onlineBH",
                             method2 == "on_prds" ~ "onlinePRDS",
                             method2 == "on_stbh" ~ "onlineStBH"),
         method_type = as.factor(case_when(str_detect(method, "online") ~ "Online",
                                           str_detect(method, "Appended") ~ "Appended",
                                           str_detect(method, "Offline") ~ "Offline",
                                           str_detect(method, "Uncorrected") ~ "Uncorrected")),
         method_type2 = as.factor(case_when(str_detect(method2, "online") ~ "Online",
                                            str_detect(method2, "Appended") ~ "Appended",
                                            str_detect(method2, "Offline") ~ "Offline",
                                            str_detect(method2, "Uncorrected") ~ "Uncorrected"))
  )
```

```{r change_prop_power_reorder1.5_supp, fig.width = 12, fig.height = 8}
ggplot(primary_data2 %>% filter(method_type != "Appended"), aes(x = pi, y = power)) +
  geom_line(aes(col = method,
                linetype = method_type),
            size = 1) +
  geom_ribbon(aes(ymin = lower_power, ymax = upper_power, fill = method), alpha = 0.2) +
  theme_bw() +
  ylim(c(0.5,1)) +
  labs(x = "Proportion of DE Genes",
       y = "Power",
       col = "Method",
       linetype = "Method Type") +
  scale_color_manual(
    values = pal,
    limits = force
  ) +
  scale_fill_manual(
    values = pal
  ) +
  scale_linetype_discrete(
    limits = force
  ) +
  guides(fill = "none") +
  theme_gen()
```

```{r change_prop_power_reorder1.5, fig.width = 12, fig.height = 8}
ggplot(primary_data2 %>% filter(pi >= 0.1,
                                method_type != "Appended",
                                method_type != "Uncorrected"),
       aes(x = pi, y = power)) +
  geom_line(aes(col = method,
                linetype = method_type),
            size = 1) +
  geom_ribbon(aes(ymin = lower_power, ymax = upper_power, fill = method), alpha = 0.2) +
  theme_bw() +
  ylim(c(0.5,1)) +
  labs(x = "Proportion of DE Genes",
       y = "Power",
       col = "Method",
       linetype = "Method Type") +
  scale_color_manual(
    values = pal,
    limits = force
  ) +
  scale_fill_manual(
    values = pal
  ) +
  scale_linetype_discrete(
    limits = force
  ) +
  guides(fill = "none") +
  theme_gen()
```

* It's evident we see that the power gains are substantial compared to the unordered batches

```{r change_prop_fdr_reorder1.5_supp, fig.width = 12, fig.height = 8}
ggplot(primary_data2 %>% filter(method_type2 != "Appended"), aes(x = pi, y = fdr)) +
  geom_line(aes(col = method2,
                linetype = method_type2),
            size = 1) +
  geom_ribbon(aes(ymin = lower_fdr, ymax = upper_fdr, fill = method2), alpha = 0.2) +
  theme_bw() +
  geom_hline(yintercept = 0.05, col = "black") +
  labs(x = "Proportion of DE Genes",
       y = "FDR",
       col = "Method",
       linetype = "Method Type") +
  scale_color_manual(
    values = pal,
    limits = force
  ) +
  scale_fill_manual(
    values = pal
  ) +
  scale_linetype_discrete(
    limits = force
  ) +
  guides(fill = "none") +
  theme_gen()
```

```{r change_prop_fdr_reorder1.5, fig.width = 12, fig.height = 8}
ggplot(primary_data2 %>%
         filter(method_type2 != "Appended",
                method_type2 != "Uncorrected",
                pi >= 0.1), aes(x = pi, y = fdr)) +
  geom_line(aes(col = method2,
                linetype = method_type2),
            size = 1) +
  geom_ribbon(aes(ymin = lower_fdr, ymax = upper_fdr, fill = method2), alpha = 0.2) +
  theme_bw() +
  geom_hline(yintercept = 0.05, col = "black") +
  labs(x = "Proportion of DE Genes",
       y = "FDR",
       col = "Method",
       linetype = "Method Type") +
  scale_color_manual(
    values = pal,
    limits = force
  ) +
  scale_fill_manual(
    values = pal
  ) +
  scale_linetype_discrete(
    limits = force
  ) +
  guides(fill = "none") +
  theme_gen()
```

* Although the naive and Appended offline approaches are less variable, we still see that naive may fail to control FDR at nominal level
* BatchStBH inflates at smaller $\pi$ when batches are "well-ordered" with more powerful datasets in beginning

```{r, eval=FALSE}
#prep PPV data
secondary_means2 <- rbindlist(all_pi_sim_data2)[,lapply(.SD, mean, na.rm = TRUE), list(pi)] %>%
  select(pi, contains("ppv")) %>%
  pivot_longer(cols = contains("ppv"),
               names_to = "method",
               names_prefix = "ppv_",
               values_to = "ppv")

secondary_lower_bounds2 <- rbindlist(all_pi_sim_data2)[,lapply(.SD, quantile, probs = 0.025, na.rm = TRUE), list(pi)] %>%
  select(pi, contains("ppv")) %>%
  pivot_longer(cols = contains("ppv"),
               names_to = "method",
               names_prefix = "ppv_",
               values_to = "ppv") %>%
  rename(lower_ppv = ppv)

secondary_upper_bounds2 <- rbindlist(all_pi_sim_data2)[,lapply(.SD, quantile, probs = 0.975, na.rm = TRUE), list(pi)] %>%
  select(pi, contains("ppv")) %>%
  pivot_longer(cols = contains("ppv"),
               names_to = "method",
               names_prefix = "ppv_",
               values_to = "ppv") %>%
  rename(upper_ppv = ppv)

secondary_data2 <- bind_cols(secondary_means2,
                             secondary_lower_bounds2 %>% select(lower_ppv),
                             secondary_upper_bounds2 %>% select(upper_ppv)) %>%
  mutate(method = case_when(method == "0.025" ~ "Uncorrected 0.025",
                            method == "0.05" ~ "Uncorrected 0.05",
                            method == "0.1" ~ "Uncorrected 0.1",
                            method == "off_bh" ~ "Offline BH",
                            method == "off_stbh" ~ "Offline StBH",
                            method == "pool_bh" ~ "Appended BH",
                            method == "pool_stbh" ~ "Appended StBH",
                            method == "on_bh" ~ "BatchBH",
                            method == "on_prds" ~ "BatchPRDS",
                            method == "on_stbh" ~ "BatchStBH"),
         method_type = as.factor(case_when(str_detect(method, "Batch") ~ "Batch",
                                           str_detect(method, "Appended") ~ "Appended",
                                           str_detect(method, "Offline") ~ "Offline",
                                           str_detect(method, "Uncorrected") ~ "Uncorrected"))
  )
```

```{r change_prop_ppv_reorder1.5_supp, fig.width = 12, fig.height = 8, eval=FALSE}
ggplot(secondary_data2 %>% filter(pi > 0), aes(x = pi, y = ppv)) +
  geom_line(aes(col = method,
                linetype = method_type),
            size = 1) +
  geom_ribbon(aes(ymin = lower_ppv, ymax = upper_ppv, fill = method), alpha = 0.2) +
  theme_bw() +
  labs(x = "Proportion of DE Genes",
       y = "PPV",
       col = "Method",
       linetype = "Method Type") +
  scale_color_manual(
    values = pal
  ) +
  scale_fill_manual(
    values = pal
  ) +
  scale_linetype_discrete(
    limits = force
  ) +
  guides(fill = "none") +
  theme_gen()
```

Let's zoom in:

```{r change_prop_ppv_reorder1.5, fig.width = 12, fig.height = 8, eval=FALSE}
ggplot(secondary_data2 %>%
         filter(pi > 0,
                !method %in% c("Uncorrected 0.025", "Uncorrected 0.05", "Uncorrected 0.1")),
       aes(x = pi, y = ppv)) +
  geom_line(aes(col = method,
                linetype = method_type),
            size = 1) +
  geom_ribbon(aes(ymin = lower_ppv, ymax = upper_ppv, fill = method), alpha = 0.2) +
  theme_bw() +
  labs(x = "Proportion of DE Genes",
       y = "PPV",
       col = "Method",
       linetype = "Method Type") +
  scale_color_manual(
    values = pal,
    limits = force
  ) +
  scale_fill_manual(
    values = pal
  ) +
  scale_linetype_discrete(
    limits = force
  ) +
  guides(fill = "none") +
  theme_gen()
```